---
title: "Rebecca N Assignment 10"
output: html_notebook
author: "Rebecca Neal"
Date: "19 April"
Version: "1.0"
---

This is a notebook for Assignment 10 focused on data wrangling

### Load in packages
```{r include=FALSE}
library(tidyverse)
library(ggplot2)
```

### Q1 Load data
```{r}
JE <- read_csv("Johnson Elementary ELA Project.csv", skip=4,
               col_names= c("Room", "Student ID", 
               "TA", "Q1", "Q2","Q3", "Q4"))
```

### Q1 Seperate Tardies and Absences
```{r}
JE <- JE %>%
  separate(TA, into = c("Tardies", "Absences"), sep = ";") 
  
```

### Q1 Clean Tardies & Absences
```{r}
JE$Tardies <- parse_integer(JE$Tardies)
JE$Absences <- parse_integer(JE$Absences)
```

### Q1 Fill in room data, drop header lines, and make Quarter and Scores variable
```{r}
JE <- JE %>%
  fill(Room) %>%
  drop_na(`Student ID`) %>%
  gather(Q1, Q2, Q3, Q4,
         key = "Quarter",
         value = "Scores")
  
```

### Q2 Write script for summary tardies and absences by room number
```{r}
JE %>%
  group_by(Room) %>%
  summarize(Absence_Mean = mean(Absences, na.rm=TRUE),
            Absence_SD = sd(Absences, na.rm = TRUE),
            Absence_Median = median(Absences, na.rm = TRUE),
            Tardy_Mean = mean(Tardies, na.rm = TRUE),
            Tardy_SD = sd(Tardies, na.rm = TRUE),
            Tardy_Median = median(Tardies, na.rm = TRUE))
            
```

### Q3 Frequency of missing data points for each quarter by room
```{r}
Missing_Data <- JE %>%
  group_by(Room, Quarter) %>%
  count(sum(is.na(Scores)))
```


### Q4 Create median score for each quarter by room number
```{r}
JE_Median <- JE %>%
  group_by(Room, Quarter) %>%
  summarize(Room_Median = median(Scores, na.rm = TRUE))
```


### Q4 Graph with median score trends across the four quarters for the fifth grade classes
```{r}
ggplot(JE_Median, aes(x = Quarter, y = Room_Median)) +
  geom_point() +
  facet_wrap(vars(Room))
  
  
```

### Q5 Graph portion of flights that are on time from NYC to ATL by carrier
### Load data
```{r}
NYC <- read_csv("NYC Flights 2013.csv")
```

### Clean data and create new variable for on_time
```{r}
NYC_ATL <- NYC %>%
  filter(dest == "ATL", !is.na(arr_delay)) %>%
  group_by(carrier) %>%
  mutate(on_time = (arr_delay <=0))
```

### Plot
```{r}
ggplot(data = NYC_ATL, mapping = aes(x=carrier)) +
  geom_bar(aes(fill = on_time), position = "fill") +
  labs(x = "Airline Carrier",
       y = "Portion of Flights On Time",
       title = "Flights On Time From NYC to ATL by Carrier") +
       scale_x_discrete(labels = c("Endeavor", "Delta", "Express Jets",
                                   "AirTran", "Envoy", "United", "SouthWest"))
```













